---
title: "Task3"
author: "Vladyslav Kushnir"
date: "26/11/2024"
format:
  html:
    embed-resources: true
editor: source
---

## Question 1 title

Question description

```{r}
df <- airquality
```
1. What are the column names of the data frame?

```{r}
colnames(df)
```
[1] "Ozone"  "Solar.R" "Wind"   "Temp"   "Month"  "Day"

2. What are the row names of the data frame?

```{r}
rownames(airquality)
```

3. Extract the first 6 rows of the data frame and print them to the console

```{r}
head(airquality,6)
```

4. Haw many observations (i.e. rows) are in this data frame?

```{r}
nrow(airquality)
```

5. Extract the last 6 rows of the data frame and print them to the console

```{r}
tail(airquality, 6)
```

6. How many missing values are in the "Ozone' column of this data frame?

```{r}
sum(is.na(airquality$Ozone))
```

7. What is the mean of the "Ozone" column in this dataset? Exclude missing values (coded as Na) from this calcualtion.

```{r}
mean(airquality$Ozone, na.rm = TRUE)
```

8. Extract the subset of rows of the data frame where Ozone values are above 31 and Temp values are above 90.

```{r}
library(dplyr)
subset_airquality <- airquality |>
  filter(Ozone >31 & Temp > 90)

print(subset_airquality)
```


